---
title: "p8105_hw3_yf2563"
author: "Yatong Feng"
date: "10/9/2020"
output: github_document
---


```{r setup, message=FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r}
data("instacart")
instacart
```

**Short description:**   
This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns.

Observations are the level of items in orders by user. There are user / order variables -- user ID, order ID, order day, and order hour. There are also item variables -- name, aisle, department, and some numeric codes. 

**Questions:**

#### 1.1. How many aisles are there, and which aisles are the most items ordered from?

```{r}
instacart %>% 
	count(aisle) %>% 
	arrange(desc(n))
```
There are 134 aisles, and fresh vegetables is the most items ordered from


#### 1.2. Make a plot that shows the number of items ordered in each aisle

- limiting this to aisles with more than 10000 items ordered. 
- Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart %>% 
	count(aisle) %>% 
	filter(n > 10000) %>% 
	mutate(
		aisle = factor(aisle),
		aisle = fct_reorder(aisle, n)
	) %>% 
	ggplot(aes(x = aisle, y = n)) + 
	geom_point() + 
  labs(
    title = "Number of Items (more than 10000) Ordered in Each Aisle"
  ) +
	theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

  
```

#### 1.3. Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>% 
	filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
	group_by(aisle) %>% 
	count(product_name) %>% 
	mutate(rank = min_rank(desc(n))) %>% 
	filter(rank < 4) %>% 
	arrange(aisle, rank) %>% 
  knitr::kable()
```

**4. Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).**

```{r, message=FALSE}
instacart %>% 
	filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
	group_by(product_name, order_dow) %>% 
	summarize(mean_hour = mean(order_hour_of_day)) %>% 
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	)
```

## Problem 2

#### 2.0. Description of the dataset

This problem uses five weeks of accelerometer data collected on a 63 year-old male with BMI 25, who was admitted to the Advanced Cardiac Care Center of Columbia University Medical Center and diagnosed with congestive heart failure (CHF). In this spreadsheet, variables activity.* are the activity counts for each minute of a 24-hour day starting at midnight.

#### 2.1. Load, tidy, and otherwise wrangle the data.

- include all originally observed variables and values; have useful variable names; 
- include a weekday vs weekend variable; 
- encode data with reasonable variable classes. 

```{r}
accel_data_path = './data/accel_data.csv'

accel_data = 
  read_csv(accel_data_path) %>%
  janitor::clean_names() %>%
  mutate(
    weekday = case_when(
    day == "Saturday" ~ "weekend",
    day == "Sunday"   ~ "weekend",
    TRUE              ~ "weekday"
    )
  ) %>%
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minute",
    names_prefix = "activity_",
    values_to = "accel") %>%
  mutate(minute = as.numeric(minute)) %>%
  rename("week_id" = week)

accel_data
```

 - Describe the resulting dataset (e.g. what variables exist, how many observations, etc).
 
```{r}
summary(accel_data)
```

Description: The dimension of this resulting dataset is `r dim(accel_data)`, which means that, there are `r dim(accel_data)[1]` observations and `r dim(accel_data)[2]` variables. The variables include `r ls(accel_data)`. `week_id` includes numbers ranging from 1 to 5, and `day_id` includes numbers ranging from 1 to 35 (each day in 5 weeks). `weekday` is weekday vs weekend variable. `minute` includes numbers ranging from 1 to 1440, which represents the original activity_1:activity_1440 (each minute of a 24-hour day starting at midnight).

#### 2.2. Make a table
Traditional analyses of accelerometer data focus on the total activity over the day. 

- aggregate accross minutes to create a total activity variable for each day
- Are any trends apparent?


```{r}
accel_table = 
  accel_data %>%
  mutate(day = forcats::
           fct_relevel(day, c("Monday", "Tuesday", "Wednesday", 
                              "Thursday", "Friday", "Saturday", "Sunday"))) %>% 
  group_by(week_id, day) %>%
  summarise(total_counts = sum(accel)) %>%
  pivot_wider(names_from = week_id,
              names_prefix = "week_",
              values_from = total_counts) %>% 
  knitr::kable(digits = 1)

accel_table
```

Trends: There is no obvious trend presents in the table. Besides, Monday of week 1 and Saturday of Week 4 and 5 have obvious lower value.

#### 2.3. Make a plot
Accelerometer data allows the inspection activity over the course of the day. 

- Make a single-panel plot that shows the 24-hour activity time courses for each day
- use color to indicate day of the week
- Describe in words any patterns or conclusions you can make based on this graph.

```{r}
accel_plot_data = 
  accel_data %>%
  mutate(day = forcats::
           fct_relevel(day, c("Monday", "Tuesday", "Wednesday", 
                              "Thursday", "Friday", "Saturday", "Sunday"))) %>%
  mutate(hour = (minute - 1) %/% 60) %>% 
  group_by(day_id, hour,day) %>%
  summarise(total_hour_accel = sum(accel))
accel_plot_data

accel_plot_data%>%
  ggplot(aes(x = hour, y = total_hour_accel, group = day_id)) +
  geom_line(aes(colour=day)) +
  labs(title = "24-hour Activity Time Courses for Each Day") + 
  xlab("Time (h)") + 
  ylab("Activity") +
  ylim(0,120000)
```

Describe: In the plot of 24-hour activity time courses, during 00:00 to 05:00, the activity in all days are relatively low. After 05:00, the data fluctuates. At around 11:00, the activity in Sundays is relatively higher.

## Problem 3

#### 3.1. Load data

- write a short description of the dataset
- noting the size and structure of the data
- describing some key variables
- indicating the extent to which missing data is an issue. 

```{r}
data("ny_noaa")
ny_noaa
```

#### 3.2. data cleaning. 

- Create separate variables for year, month, and day. 
- Ensure observations for temperature, precipitation, and snowfall are given in reasonable units. 
- For snowfall, what are the most commonly observed values? Why?


#### 3.3. Make a plot

- Make a two-panel plot showing the average max temperature in January and in July in each station across years. 
- Is there any observable / interpretable structure? Any outliers?


#### 3.4. Make a plot

- (i) tmax vs tmin for the full dataset (not scatterplot)
- (ii) make a plot showing the distribution of snowfall values greater than 0 and less than 100 separately by year.
- commenting on the results


